---
title: "progress-report-sambonn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
library(Lahman)
head(HallOfFame, 3)

?Lahman

data(HallOfFame)
head(HallOfFame)

str(HallOfFame)


HallOfFame %>% 
  ggplot(aes(x = yearID, fill = inducted)) +
  geom_bar() +
  xlim(c(1936, 2024))



library(rvest)
url <- "https://www.baseball-reference.com/awards/hof_2025.shtml"
html <- read_html(url)
tables <- html_table(html)


head(tables[[1]], 5)


#If Needed
data <- tables[[1]]
actual_col_names <- data[1, ]
colnames(data) <- actual_col_names
data <- data[-1, ]
head(data, 3)

head(data)

str(data)

data$Votes <- as.numeric(data$Votes)

data$Yrs <- as.numeric(data$Yrs)

newhof<-data

head(newhof)
newhof$Votes <- as.numeric(newhof$Votes)
newhof$Yrs <- as.numeric(newhof$Yrs)

view(newhof)

newhof$YoB <- str_extract(newhof$YoB, "\\d+")
newhof$YoB <- as.numeric(newhof$YoB)

newhof <- newhof |>
  select(
    Name,
    Votes
  )

newhof <- newhof |>
  mutate(
    yearID = 2025,
    votedBy = "BBWAA",
    ballots = 394,
    needed = 296,
    category = "Player",
    inducted = ifelse(Votes>=296, "Y", "N"),
    needed_note = NA
  )

newhof <- newhof %>%
  mutate(Name = stri_trans_general(Name, "Latin-ASCII"))


newhof <- newhof %>%
  mutate(Name = gsub("^X-\\s*", "", Name, ignore.case = TRUE))


view(newhof)

people_expanded <- People |>
  mutate(playerName = paste(nameFirst, nameLast))

newhof <- newhof %>%
  left_join(
    people_expanded %>% select(playerID, playerName),
    by = c("Name" = "playerName")
  )

newhof <- newhof %>%
  select(playerID, yearID, votedBy, ballots, needed, votes = Votes,
         inducted, category, needed_note)
HallOfFame <- rbind(HallOfFame,newhof)

view(HallOfFame)


HallOfFame %>% 
  ggplot(aes(x = yearID, fill = inducted)) +
  geom_bar() +
  xlim(c(1936, 2025))






Checking <- read.csv("HallOfFame.csv")

head(Checking)

Checking %>% 
  ggplot(aes(x = yearID, fill = inducted)) +
  geom_bar() +
  xlim(c(1936, 2025))
  
